A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-03-24 draft/ms_v10.tex
Close to finishe

% Packages
\usepackage{deluxetable}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

@@

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$} 
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

@@

\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Halos of Massive Central Galaxies}

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        HSC collaboration$^{3}$   
        \\ \\
        % List of institutions
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }

\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

%        \author{Song Huang\altaffilmark{1} 
%        Alexie Leauthaud\altaffilmark{1}, 
%        Kevin Bundy\altaffilmark{1},
%        Michael Strauss\altaffilmark{2},
%        Yen-Ting Lin\altaffilmark{3},
%        Rachel Mandelbaum\altaffilmark{4}
%        }
%\altaffiltext{2}{Princeton University Observatory, 
%    Peyton Hall, Princeton, NJ 08544, USA}
%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
%    P.O.~Box 23--141, Taipei 10617, Taiwan}
%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%

\begin{document}

@@

    The promising hierarchical assembly scenario of massive galaxies suggest the 
    structure of these galaxies should depend on their environments or halo mass.
    Yet, at low redshift, observations find no clear evidence for that. 
    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
    out to the very outskirt, and detect subtle, but robust structural differences 
    that depend on halo mass for central galaxies at high mass end. 
    With the help of the \redm{} catalog, we separate these massive galaxies 
    into centrals of halos that are more and less massive than 
    $M_{\mathrm{Halo}}\sim 10^{14} M_{\odot}$.
    For centrals with similar stellar mass within 100 kpc, the ones from 
    more massive halos on average have slightly more flattened inner profile 
    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
    proxy of the mass of the in-situ component, the massive centrals of more  
    massive halos show much more significant outer stellar envelopes.    
    We also see that these two samples of massive galaxies follow slightly 
    different mass-size relation and the relationship between the stellar mass 
    within 100 and 10 kpc.
    Such differences in structure are broadly consistent with the expectation that
    central galaxy from more massive halo should have more complex merging history.
    These results highlight the importance of deep photometry in the study of 
    the assembly history of massive galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z\sim 0.4$. 
          All of these galaxies have the same mass within a 10 kpc aperture 
          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates 10 kpc.
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          $\sim 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter halos 
    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
    questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z\sim 0$ massive early-type galaxies (ETGs) 
    undergo a rapid growth phase at $z\sim 2$ triggered either by disk instabilities 
    or gas rich mergers (e.g\citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

@@

    According to this two-phase formation scenario, the late time growth of massive ETGs 
    is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A natural prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''
    \footnote{There are different observational definitions of "environment". 
    In this paper, we use the term ``environment'' and halo mass interchangeably}.

@@

    In this paper, we take advantage of new high-resolution (median 
    FWHM$\sim 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program (SSP; \citealt{HSCDR1; will be referred as the HSC survey} to revisit the 
    question of the environmental dependence in the mass-size relation. 
    The goal of this paper is to compare the \mden{} profiles and structural scaling 
    relations of massive central galaxies in both low and high mass dark matter halos. 
    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample ($\sim 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using $\sim 100$ square degree of data from the 
    HSC wide layer.

@@

    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            The dash-line shows the surface brightness profile after correcting the 
            background. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the masked $i$-band image of this galaxy with the isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}\sim 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ 
    in 5 broad bands ($grizY$) to a limiting depth of $r \sim 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 0.6"), 
    and the wide area, the HSC survey represents a tremendous data set to perform a 
    large statistical study of the surface brightness profiles of ETGs out to large radii.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

@@

    For objects without a spectroscopic redshift, we match them with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.3 \leq z \leq 0.5$. The accuracy of the red-sequence photo-$z$ is sufficient 
    (median $|z_{\lambda} - z_{\mathrm{Spec}}| \sim 0.01$ for the ones with a 
    spec-$z$) for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (will be referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS "legacy" LRG samples provide the majority of 
    spec-$z$. 
    By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z\sim 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z\sim 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.

@@

    Our study focuses on galaxies located at the center of their dark matter halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    The \redm{} catalog therefore helps us group massive central galaxies into samples 
    with different average \mhalo{}. 
    The reliable candidates of central galaxies in the \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) form a nice sample of massive central galaxies 
    that live in very massive halos \alexie{Let's talk about this phrase.}.

>>>>

% Packages
\usepackage{deluxetable}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{url}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

@@

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{${\sim}$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{${\sim}$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over {\sim} \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over {\sim} \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$} 
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Kevin Bundy,$^{3,1}$
        Jenny Greene,$^{4}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Rachel Mandelbaum,$^{6}$
        Michael Strauss,$^{4}$
        and HSC collaboration$^{7}$   
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{6}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{7}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%
\begin{document}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    For the first time, we conclusively show that at fixed stellar mass, massive central 
    galaxies display mass density profiles that are not self similar and which 
    present subtle but systematic differences that correlate with \mhalo{}. 
    On average, massive central galaxies in more massive halos have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
    envelopes. 
    These differences translate into a clear environmental dependence of the mass-size 
    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
    at fixed \mtot{}. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    Furthermore, because galaxies in larger halos have more extended envelopes, 
    the amount of light that is missed will be halo mass dependent. 
    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
    in the amplitude of stellar profiles at 100 kpc. 
    We argue that ``cD'' galaxies represent the tail end of a distribution and 
    are not a distinct class of massive galaxies. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these galaxies have the same mass within a 10 kpc aperture 
          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates 10 kpc.
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed ``inner'' mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          ${\sim} 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter halos 
    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
    questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

@@

    According to this two-phase formation scenario, the late time growth of massive ETGs 
    is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A natural prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''
    \footnote{There are different observational definitions of ``environment''. 
    In this paper, we use the term ``environment'' and halo mass interchangeably}.

@@

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to revisit the 
    question of the environmental dependence in the mass-size relation. 
    The goal of this paper is to compare the \mden{} profiles and structural scaling 
    relations of massive central galaxies in both low and high mass dark matter halos. 
    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample (${\sim} 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer.

@@

    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover ${\sim} 1400$ deg$^2$ 
    in 5 broad bands ($grizY$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec), and the wide area, the HSC survey represents a tremendous data set to 
    perform a large statistical study of the surface brightness profiles of ETGs out to 
    large radii.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

@@

    For objects without a spectroscopic redshift, we match them with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.3 \leq z \leq 0.5$. The accuracy of the red-sequence photo-$z$ is sufficient 
    (median $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with a 
    spec-$z$) for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (will be referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. 
    By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z{\sim} 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.

@@

    Our study focuses on galaxies located at the center of their dark matter halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    The \redm{} catalog therefore helps us group massive central galaxies into 
    samples with different average \mhalo{}. 
    We will use the central galaxies of \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
    live in massive halos.
